RDF Validation Requirements - Evaluation and Logical Underpinning

### 2015-07-13 paper/RDF validation requirements/RDF validation requirements.tex
classification

*Subsumption & $\sqsubseteq$ & sub-classes \\
*Class Equivalence & $\equiv$ & equivalent classes \\
*Sub Properties & $\sqsubseteq$ & sub-properties \\
*Property Domain & $\exists$, $\sqsubseteq$ & property domain \\
*Property Range & $\sqsubseteq$, $\forall$ & property range \\
*Inverse Object Properties & inverse & inverse properties \\
%*Symmetric Object Properties & $\equiv$, inverse & symmetric \\
*Symmetric Object Properties & symmetric & symmetric properties \\
%*Asymmetric Object Properties & $\sqsubseteq$, inverse & asymmetric \\
*Asymmetric Object Properties & asymmetric & asymmetric properties \\
%*Reflexive Object Properties & $\exists$, $\sqsubseteq$ & \textcolor{green}{reflexive} \\
*Reflexive Object Properties & reflexive & reflexive properties \\
%*Irreflexive Object Properties & $\exists$, $\neg$, $\sqsubseteq$ & irreflexive \\
*Irreflexive Object Properties & reflexive, $\neg$ & irreflexive properties \\
Disjoint Properties & $\sqsubseteq$, $\neg$ & $\ne$ \\
Disjoint Classes & $\sqcap$, $\sqsubseteq$ & $\ne$ \\
Context-Sp. Property Groups & $\sqcap$ & property group \\
Context-Sp. Inclusive OR of P. & $\sqcup$ & inclusive or of properties \\
Context-Sp. Inclusive OR of P. Groups & $\sqcup$, $\sqcap$ & inclusive or of property groups, \\
                                                          && property group \\
Recursive Queries & - & recursive \\
Individual Inequality & $\ne$ & \\
*Equivalent Properties & $\equiv$ & equivalent properties \\
Property Assertions & = or $\ne$ & \\
Data Property Facets & - & XSD or SPARQL constraining facets \\
                        && examples: regex, xsd:pattern, ... \\
Literal Pattern Matching & - & regex or xsd:pattern \\
Negative Literal Pattern Matching & - & regex or xsd:pattern, $\neg$ \\ 
*Object Property Paths & $\sqsubseteq$ & property paths \\
*Intersection & $\sqcap$ & intersection \\
*Disjunction & $\sqcup$ & disjunction \\
*Negation & $\neg$ & negation \\
*Existential Quantification & $\exists$ & existential quantification \\
*Universal Quantification & $\forall$ & universal quantification \\
*Minimum Unqualified Cardinality & $\geq$ & \\
*Minimum Qualified Cardinality & $\geq$ & \\
*Maximum Unqualified Cardinality & $\leq$ & \\
*Maximum Qualified Cardinality & $\leq$ & \\
*Exact Unqualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
*Exact Qualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
*Transitive Object Properties & $\sqsubseteq$ & transitive properties \\
Context-Sp. Exclusive OR of P. & $\neg$, $\sqcap$, $\sqcup$ & XOR of properties \\
Context-Sp. Exclusive OR of P. Groups & $\neg$, $\sqcap$, $\sqcup$ & XOR of property groups \\
                                                                 & & property group \\
Allowed Values & $\sqcup$ & allowed values \\
Not Allowed Values & $\sqcup$, $\neg$ & not allowed values \\
%Literal Ranges & $\geq$, $\leq$, $\sqcap$ &  \\ 
Literal Ranges & - & xsd:minInclusive \\
               & & xsd:maxInclusive \\
%Negative Literal Ranges & $\geq$, $\leq$, $\sqcap$, $\neg$ & \\  
Negative Literal Ranges & - & xsd:minInclusive \\
                        & & xsd:maxInclusive \\
Required Properties & $\exists$ & required properties \\

>>>>

*Subsumption & $\sqsubseteq$ & sub-classes \\
*Class Equivalence & $\equiv$ & equivalent classes \\
*Sub Properties & $\sqsubseteq$ & sub-properties \\
*Property Domains & $\exists$, $\sqsubseteq$ & property domain \\
*Property Ranges & $\sqsubseteq$, $\forall$ & property range \\
*Inverse Object Properties & inverse & inverse properties \\
%*Symmetric Object Properties & $\equiv$, inverse & symmetric \\
*Symmetric Object Properties & symmetric & symmetric properties \\
%*Asymmetric Object Properties & $\sqsubseteq$, inverse & asymmetric \\
*Asymmetric Object Properties & asymmetric & asymmetric properties \\
%*Reflexive Object Properties & $\exists$, $\sqsubseteq$ & \textcolor{green}{reflexive} \\
*Reflexive Object Properties & reflexive & reflexive properties \\
%*Irreflexive Object Properties & $\exists$, $\neg$, $\sqsubseteq$ & irreflexive \\
*Irreflexive Object Properties & reflexive, $\neg$ & irreflexive properties \\
Disjoint Properties & $\sqsubseteq$, $\neg$ & $\ne$ \\
Disjoint Classes & $\sqcap$, $\sqsubseteq$ & $\ne$ \\
Context-Sp. Property Groups & $\sqcap$ & property group \\
Context-Sp. Inclusive OR of P. & $\sqcup$ & inclusive or of properties \\
Context-Sp. Inclusive OR of P. Groups & $\sqcup$, $\sqcap$ & inclusive or of property groups, \\
                                                          && property group \\
Recursive Queries & - & recursive \\
Individual Inequality & $\ne$ & \\
*Equivalent Properties & $\equiv$ & equivalent properties \\
Property Assertions & = or $\ne$ & \\
Data Property Facets & - & XSD or SPARQL constraining facets \\
                        && examples: regex, xsd:pattern, ... \\
Literal Pattern Matching & - & regex or xsd:pattern \\
Negative Literal Pattern Matching & - & regex or xsd:pattern, $\neg$ \\ 
*Object Property Paths & $\sqsubseteq$ & property paths \\
*Intersection & $\sqcap$ & intersection \\
*Disjunction & $\sqcup$ & disjunction \\
*Negation & $\neg$ & negation \\
*Existential Quantification & $\exists$ & existential quantification \\
*Universal Quantification & $\forall$ & universal quantification \\
*Minimum Unqualified Cardinality & $\geq$ & \\
*Minimum Qualified Cardinality & $\geq$ & \\
*Maximum Unqualified Cardinality & $\leq$ & \\
*Maximum Qualified Cardinality & $\leq$ & \\
*Exact Unqualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
*Exact Qualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
*Transitive Object Properties & $\sqsubseteq$ & transitive properties \\
Context-Sp. Exclusive OR of P. & $\neg$, $\sqcap$, $\sqcup$ & XOR of properties \\
Context-Sp. Exclusive OR of P. Groups & $\neg$, $\sqcap$, $\sqcup$ & XOR of property groups \\
                                                                 & & property group \\
Allowed Values & $\sqcup$ & allowed values \\
Not Allowed Values & $\sqcup$, $\neg$ & not allowed values \\
%Literal Ranges & $\geq$, $\leq$, $\sqcap$ &  \\ 
Literal Ranges & - & xsd:minInclusive \\
               & & xsd:maxInclusive \\
%Negative Literal Ranges & $\geq$, $\leq$, $\sqcap$, $\neg$ & \\  
Negative Literal Ranges & - & xsd:minInclusive \\
                        & & xsd:maxInclusive \\
Required Properties & $\exists$ & required properties \\
